Networked Character Devices

### 2011-12-11 report/paper.tex
Added future work section

As of this writing, we have completed a partial implementation of
the Network Character Devices system. Current functionality includes:

@@

>>>>

As of this writing, we have completed a partial implementation of
the Network Character Devices system (Figure
\ref{fig:system-working}). Current functionality includes:

@@

As Figure \ref{fig:system-working} shows, there are still several
portions of the NCD system that need implemented before the system is
ready for production-level use. In particular, the top priorities
currently are:

\begin{packed_item}
\item Add multi-device, multi-server support
\item Add kernel sub-system handler layer (HID, etc)
\item Add device protection and removal capabilities to server system
\item Add advertisement protocol
\item Separate networking and memory-intensive code from client kernel module
\end{packed_item}

The current NCD system only support a single device per server and per
client. To be truly useful and to enable the construction of the
kinds of system we envision NCD being used for (Section
\ref{potentialuses}), we must at least
expand the client-side
system to support importing an arbitrary number of devices from one
or more servers. Ideally, servers should also be capable of serving
multiple devices, but this is of less importance than multi-device
client handling.

As we mentioned in Section \ref{sec:challenges}, some modern device
drivers bypass the traditional Character Device file interface. Thus, we
must expand the NCD system to accommodate the additional interfaces and
subsystems that are commonly in use. This includes special import
handling for in-kernel subsystems like the X Server and HID
subsystems, as well as generalized support for sysfs and procfs import
and export.

We also plan to add a means for device protection and exclusion to
the NCD system. This will include both the need to remove exported
devices from use by local server-side operating systems as well as controlling
the number of clients that can connect to a single exported
device. Controlling the latter point will require a per-device
definition, probably provided as part of the export configuration, of
how many clients may simultaneously utilize each device. Some devices will
require exclusive access while other may be capable of handling read
and/or write request from multiple clients simultaneously.

Since large scale NCD deployments may include thousands of exported
devices, the NCD system requires the addition of an advertisement and
discovery protocol so that client may ascertain what resources are
currently available for import. Such a system will need to provide
information about what devices are available, as well as metadata
describing the basic characteristics of a given device.

Finally, the current client-side NCD implementation performs both direct
network access and memory-intensive processing directly in the kernel
code. For security reasons, it is desirable to separate the direct
network communication from the kernel code to user-space code where
the repercussions of a security breach as less extreme.
For performance reasons, it is desirable to move memory
intensive operations from the kernel code (where they are limited to
the available kernel memory space) to user-space code where the memory
availability is far greater and the use restrictions more relaxed. To
solve these issues, we
foresee building a client-daemon that will handle the bulk to the
client-side operations and that will, in turn, communicate directly with
a more minimal client kernel module only when necessary.
